Multispecies survey for diet comp

### 2020-12-08 SurveyDietCompTest.Rmd
add comparison of low and high variance without bias

samp4 <- sample_diet(survey_cons, fgs, unidprey = 0.3, alphamult = 10000)

@@

@@

Here we compare survey diet comp with no bias and variance, with some bias (unidprey = 0.3 or up to 30% of each prey proportion could be set to unidentified) and extremely low to moderate Dirichlet observation error (alphamult = 10000000 and alphamult = 10000):

@@

### Biased survey diet, low and high observation error {.tabset}

@@

for(i in 1:length(preds)) {
  cat("  \n####",  as.character(preds[i]),"  \n")
  print(plotdiet(dat = filter(samp3, species %in% preds[i]), namedat = "Biased survey diet", compdat = filter(samp4, species %in% preds[i]), namecomp = "Bias and variance survey diet")) 
  cat("  \n")
}
```

@@

>>>>

samp4 <- sample_diet(survey_cons, fgs, unidprey = 0.3, alphamult = 10)

@@

samp6 <- sample_diet(survey_cons, fgs, unidprey = 0, alphamult = 10)

@@

Here we compare survey diet comp with no bias and variance (unidprey = 0 and alphamult = 10000000) to survey diet with some bias (unidprey = 0.3 or up to 30% of each prey proportion could be set to unidentified, and alphamult = 10000000):

@@

### Unbiased survey diet, low and high observation error {.tabset}
Here we compare survey diet comp with no bias or variance (unidprey = 0 and alphamult = 10000000), with no bias and high Dirichlet observation error (unidprey = 0 and alphamult = 10):

@@

for(i in 1:length(preds)) {
  cat("  \n####",  as.character(preds[i]),"  \n")
  print(plotdiet(dat = filter(samp1, species %in% preds[i]), namedat = "No variance survey diet", compdat = filter(samp6, species %in% preds[i]), namecomp = "High variance survey diet")) 
  cat("  \n")
}

@@

### Biased survey diet, low and high observation error {.tabset}
Last we compare survey diet comp with some bias (unidprey = 0.3 or up to 30% of each prey proportion could be set to unidentified) and low observation error (alphamult = 1000000) to the same bias and high Dirichlet observation error (alphamult = 10):

for(i in 1:length(preds)) {
  cat("  \n####",  as.character(preds[i]),"  \n")
  print(plotdiet(dat = filter(samp3, species %in% preds[i]), namedat = "Biased survey diet", compdat = filter(samp4, species %in% preds[i]), namecomp = "Bias and high variance survey diet")) 
  cat("  \n")
}
```
